XXX

### 2012-03-24 paper/engNERwiki.tex
Evaluation elso resze megirva

\section{Creation of the Hungarian Corpus}
\label{sec:hun}

Hungarian differs from English not only as a language, but in data and tool coverage and NER practices as well.
The procedure described in the previous section was used to generate the Hungarian corpus as well. However, the differences between English and Hungarian prompted XXX several modifications in its steps. In this section we describe how the algorithm was adapted to Hungarian. XXX!!!

@@

\subsection{Training Corpus}

@@

@@

% vs. ConLL / Szeged
% Corpus sizes, performance, tagging conventions

% Hun -> not utf-8, loss of precision?

Having the obvious advantages, an automatically generated corpus can not serve as a gold standard dataset. Then what can we do with these so called "silver standard corpora" (SSC)? They can be very useful for improving NER in more ways: (a) for less commonly used languages, they can serve as training corpora in absence of gold standard datasets; (b) they can serve as (supplementary or independent) training sets for domains differing from newswire; (c) they can be sources of huge entity lists, and (d) feature extraction.

Sentences without any entities are retained as well, so that the corpus mirrors (XXX the distribution of entities in the corpus mirrors their distribution in Wikipedia?) the distribution of entities in Wikipedia as closely as possible; this is also in line with how the ConLL corpus is assembled. (XXX or is it)

measuring Wikipedia's inconsistency using n-gram tag variation (\cite{Nothman:09})
ez jó mérőszám lehet a gold standard korpuszok összehasonlítására
használhatjuk fordítva is: ha egy adott nucleus ugyanolyan n-gram környezetben nagyon sokszor van X-ként taggelve, és kevésszer Y-ként, akkor az Y-okat is átcsinálhatnánk X-szé

@@

>>>>

\section{Creating the Hungarian Corpus}
\label{sec:hun}

The procedure described in the last section was used to generate the Hungarian corpus as well. However, the differences between English and Hungarian prompted XXX several modifications in its steps. In this section we describe how the algorithm was adapted to Hungarian. XXX!!!

@@

@@

according to the Szeged NER guideline

@@

% vs. ConLL / Szeged
% Corpus sizes, performance, tagging conventions
% Hun -> not utf-8, loss of precision?
%measuring Wikipedia's inconsistency using n-gram tag variation (\cite{Nothman:09})
%ez jó mérőszám lehet a gold standard korpuszok összehasonlítására
%használhatjuk fordítva is: ha egy adott nucleus ugyanolyan n-gram környezetben nagyon sokszor van X-ként taggelve, és kevésszer Y-ként, akkor az Y-okat is átcsinálhatnánk X-szé

Having the obvious advantages, an automatically generated corpus can not serve as a gold standard dataset. Then what can we do with these so called "silver standard corpora" (SSC)? They can be very useful for improving NER in more ways: (a) for less resourced languages, they can serve as training corpora in absence of gold standard datasets; (b) they can serve as (supplementary or independent) training sets for domains differing from newswire; (c) they can be sources of huge entity lists, and (d) feature extraction.

To evaluate our corpora we used a maximum entropy NE-tagger \cite{Varga:07}, which was originally developed for labeling NEs in Hungarian texts, but it can be tuned for different languages, as well. The feature set was as follows:

\begin{itemize}
\item gazetteer features;
\item sentence start and end position;
\item Boolean-valued orthographic properties of the word form;
\item string-valued surface properties of the word form;
\item morphological information.
\end{itemize}

We used the CoNLL standard method for evaluation. According to this, an automatic labeling is correct if it gives the same start and end position, and the same NE class, as the gold standard. Based on this, precision and recall can be calculated, and the F-measure, as usual, the harmonic mean of these two values.

\subsection{Wikipedia data}

Our automatic annotation process retain all of the Wikipedia sentences, which remained after our two-fold filtering method. Thus sentences without NEs are also parts of the whole corpus. The rationale behind this is that we wanted to reserve the original distribution of names in Wikipedia as much as possible. However, after further investigation of NE density in our Wikipedia corpora and gold standard corpora (see table \ref{size}), we decided the sentences without NEs not to include in evaluation datasets.

\begin{table*}[ht]
\begin{center}
\begin{tabular}{lllllll}
\hline  & \bf enwiki & \bf enwiki filtered & \bf CoNLL & \bf huwiki & \bf huwiki filtered  & \bf Szeged NER \\ \hline
token & 60,520,819 & 21,718,854 & 302,811 &  19,108,027 & 3,512,249  & 225,963\\
NE & 3,169,863 & 3,169,863 & 50,758 & 456,281 & 456,281  & 25,896\\
NE density & 5.23\% & 14.59\% & 16.76\% & 2.38\% & 12.99\%  & 11.46\%\\
\hline
\end{tabular}
\end{center}
\caption{\label{size} Corpus size and NE-density. }
\end{table*}

%Sentences without any entities are retained as well, so that the corpus mirrors (XXX the distribution of entities in the corpus mirrors their distribution in Wikipedia?) the distribution of entities in Wikipedia as closely as possible; this is also in line with how the ConLL corpus is assembled. (XXX or is it)

\subsection{Experiments}

We evaluated our corpora against (a) itself (splitted into train and test sets); (b) manually annotated English and Hungarian corpora.

\subsection{Results}

@@

\bibitem[\protect\citename{Varga and Simon}2007]{Varga:07}
Dániel Varga and Eszter Simon.
\newblock 2007.
\newblock Hungarian named entity recognition with a maximum entropy approach.
\newblock {\em Acta Cybernetica}, 18: 293--301.
